Search for WIMP Inelastic Scattering Off Xenon Nuclei With XENON100 Data

### 2017-01-20 Inelastic/analysis.tex
fixed_typos_and_some_text_added_more_comments_in_red

This analysis is performed using XENON100 Run-II science data, which corresponds to a data set with an exposure of 224.6~live days. The detector response to
ERs has been characterised with $^{60}$Co and $^{232}$Th calibration sources, while the response to NRs was calibrated with an $^{241}$AmBe $(\alpha,n)$-source. This fast neutron source gives rise to elastic and inelastic neutron-nucleus scatters, and can thus be employed to define the expected signal region for inelastic WIMP-nucleus scatters.

@@

As explained in Section~\ref{sec:intro}, the inelastic scattering of a WIMP with a $^{129}$Xe nucleus produces an energy deposit via a NR with subsequent emission of  
a 39.6\,keV de-excitation photon. The largest fraction of the energy released in the event is via an ER, due to the emitted photon which loses its energy in the LXe.
This represents an unusual signature compared to the one expected from an elastic scatter, and brings the signal region to overlap with the ER background region.
The selected region of interest (ROI) for this analysis surrounds the 39.6\,keV xenon line in the cS1-cS2 plane and is further divided into
sub-regions, as shown in Figures~\ref{fig:SR} and~\ref{fig:SR2}.  These sub-regions were defined such as to contain roughly a similar number of expected background events in each region. The control regions CR1 and CR2 are chosen to be as close as possible to the signal regions,  and are used as cross check of the background shape distribution.

Apart from the condition to occur in the defined region of interest in the cS2-cS1-plane, valid events are required to fulfil several selection criteria, 
which can be summarised as follows: basic data quality cuts, energy selection and S2 threshold cut, veto cut for events with energy release in the detector's active LXe shield, 
selection of single-scatter events and of a predefined fiducial volume.

This analysis closely follows the event selection criteria described in detail in \cite{Aprile:2012vw} for Run-II, with only a few exceptions reported in what follows. 
The cut on the width of the S2 signal as a function of drift time (where the maximal drift time is 176\,$\mu$s and the width values range from $\sim$1-2\,$\mu$s) has been optimised on a sample of events selected from the 39.6\,keV line and set to a 95\% acceptance on these. This cut ensures that the S2-signal width is consistent with the $z$-position calculated from the observed time difference between the S1 and S1 signals. Events are required to be single-scatters by applying a threshold cut on the size of the 
second largest S2 peak. For this analysis, the threshold has been optimised to 160\,PE and set constant as function of S2 signal size. 
Finally, the chosen fiducial volume corresponds to 34\,kg of liquid xenon.

\begin{figure}[t!]
  \includegraphics[width=\linewidth]{images/bkg_in_sr.png}
  \caption{Signal (1-9) and control (CR1 and CR2) regions for the inelastic WIMP-$^{129}$Xe interaction in the cS2 versus cS1 plane. Their definition is given in the text.}
  \label{fig:SR}
\end{figure}

@@

The detector response to inelastic WIMP-$^{129}$Xe interactions was simulated using an empirical signal model.
The total deposited energy is divided into two independent contributions: one coming from the 39.6\,keV de-excitation photon and the other  from  
the simultaneous nuclear recoil of the xenon atom. The detected light (S1) and charge (S2) signals are simulated separately for each of the two contributions 
and then added together. This is due to the fact that the light and charge yields depend on the type of interaction (ER vs. NR), and on the deposited energy.

The distribution of an ER induced by the de-excitation photon in the cS1-cS2 plane  is simulated assuming a two dimensional normal probability distribution function (pdf), $f(cS1_{er},cS2_{er})$, 
described (apart from a constant normalisation factor) by the following equation:

@@

The same model is used to predict the charge yield at 39.6\,keV, which is afterwards scaled according to the detector's secondary scintillation gain $Y$. 
 The latter is determined from detector's response to single electrons~\cite{SingleE}.
The energy resolution at 39.6\,keV in cS1 and cS2 has been measured to be 15.8\% and 14.7\%, respectively, and is used to extract the standard 
deviations $\sigma_{cs1}$, $\sigma_{cs2}$.  The correlation parameter is assumed to be independent of energy (at least in the considered narrow energy range) and measured
using the 164\,keV line from the decay of the $^{131m}$Xe isomer ($T_{1/2}$=11.8\,d) produced during the  $^{124}$AmBe run. This $\gamma$-line is chosen because it allows to disentangle efficiently the contribution from the nuclear recoil. The measured correlation coefficient is $\rho \, = \, -0.45 \pm 0.10$.

@@

The pdf of the ER and NR contributions are then convoluted together to obtain the overall pdf of the expected signal.
A 2D (cS1 versus cS2) acceptance map is applied to the signal pdf to reproduce data selection effects. Acceptances are computed separately for each selection 
criteria using the $^{124}$AmBe calibration sample. Other selections such as the liquid xenon veto cut, and the single-scatter interaction represent an exception  and 
a dedicated computation has been performed in these cases. The combined acceptance  of all selection criteria in the region of interest averages to $\sim$$(0.80\pm0.05)$. 
Figure~\ref{fig:SR} shows an example of fully simulated signal model for a WIMP mass of 100\,GeV/c$^2$.

The signal simulation procedure has been validated by reproducing the 39.6\,keV xenon line from interactions due to neutrons from the 
$^{124}$AmBe source and comparison to data. For this comparison, the proper  $^{124}$AmBe nuclear recoil and acceptances
were simulated. The simulated events were in agreement  with calibration data within statistical uncertainties. 
{\textcolor{red} {Should we show an example, namely a figure from the signal model note?}}

@@

The expected background is modelled using data from the $^{60}$Co calibration campaign, which are assumed to well represent the background density distribution 
in the cS1-cS2 plane. The calibration sample yields  about $2.2\times10^4$ events in the ROI; these are then scaled to the science data according to a measured scale 
factor $\tau_{bkg}$. This scale factor, which is merely the ratio between the data and calibration sample yields, is measured in the two control regions shown in Figure~\ref{fig:SR} and labelled CR1 and CR2. The two control 
regions give compatible results and the computed average is $\tau_{bkg} \, =  \, 0.034 \pm 0.002 $, where the reported uncertainty 
is of statistical nature only.

>>>>

This analysis is performed using XENON100 Run-II science data, with 224.6~live days of data taking. The detector's response to ERs has been characterised with $^{60}$Co and $^{232}$Th calibration sources, while the response to NRs was calibrated with an $^{241}$AmBe $(\alpha,n)$-source. This fast neutron source gives rise to elastic and inelastic neutron-nucleus scatters, and can thus be employed to define the expected signal region for inelastic WIMP-nucleus scatters.

@@

As explained in Section~\ref{sec:intro}, the inelastic scattering of a WIMP with a $^{129}$Xe nucleus is expected to produce an energy deposit via a NR with subsequent emission of  
a 39.6\,keV de-excitation photon. The largest fraction of the energy released in the event is via an ER, due to the emitted photon which loses its energy in the LXe.
This represents an unusual signature compared to the one expected from an elastic scatter, and brings the signal region to overlap with the ER background region.
{\textcolor{red} {Should we mention that AmBe data is used here, to define these regions? And should we provide somewhere the used energy ranges in cS1 and cS2?}}
The selected region of interest (ROI) for this analysis surrounds the 39.6\,keV xenon line in the cS1-cS2 plane and is further divided into
sub-regions, as shown in Figures~\ref{fig:SR} and~\ref{fig:SR2}.  These sub-regions were defined such as to roughly contain a similar number of expected background events in each region. The control regions (denoted as CR1 and CR2 in the figures), are selected to be as close as possible to the signal regions,  and are used for cross checks of the background shape distribution.

Apart from the condition to occur in the defined region of interest in the (cS2,cS1)-plane, valid events are required to fulfil several selection criteria, 
which can be summarised as follows: basic data quality cuts, energy selection and S2 threshold cut, veto cut for events with energy release in the detector's active LXe shield, 
selection of single-scatter events and of a predefined fiducial volume.  Our analysis closely follows the event selection criteria described in detail in \cite{Aprile:2012vw} for Run-II, with only a few exceptions, as explained in the following. 
The cut on the width of the S2 signal as a function of drift time (where the maximal drift time is 176\,$\mu$s and the width values range from $\sim$1-2\,$\mu$s) has been optimised on a sample of events selected from the 39.6\,keV line and set to a 95\% acceptance on these. This cut ensures that the S2-signal width is consistent with the $z$-position calculated from the observed time difference between the S1 and S1 signals. Events are required to be single-scatters by applying a threshold cut on the size of the 
second largest S2 peak. For this analysis, the threshold has been optimised to 160\,PE and set constant as function of S2 signal size. 
Finally, the chosen fiducial volume corresponds to 34\,kg of liquid xenon, which is identical to the one used for the elastic scattering channel~\cite{Aprile:2012vw}.

\begin{figure}[t!]
  \includegraphics[width=\linewidth]{images/bkg_in_sr.png}
  \caption{Signal (1-9) and control (CR1 and CR2) regions for the inelastic WIMP-$^{129}$Xe interaction in the cS2 versus cS1 plane. Their definition is given in the text. {\textcolor{red} {We should also write which data is shown here; if this is the first plot in the paper, it may not be clear why the signal and control regions are where they are...}}}
  \label{fig:SR}
\end{figure}

@@

The detector response to inelastic WIMP-$^{129}$Xe interactions was simulated using an empirical signal model.
The total deposited energy is divided into two independent contributions: one coming from the 39.6\,keV de-excitation photon and the other  from  
the simultaneous nuclear recoil of the xenon atom. The detected light (S1) and charge (S2) signals are simulated separately for each of the two contributions 
and then added together. This recipe has been followed  because the light and charge yields depend both on the type of interaction (ER vs. NR), and on the deposited energy.

The distribution of an ER induced by the de-excitation photon in the (cS1,cS2)-plane  is simulated assuming a two dimensional normal probability distribution function (pdf), $f(cS1_{er},cS2_{er})$, 
described (apart from a constant normalisation factor) by the following equation:

@@

The same model is used to predict the charge yield at 39.6\,keV, which is then scaled according to the detector's secondary scintillation gain $Y$. 
 The latter is determined from detector's response to single electrons~\cite{SingleE}.
The energy resolution at 39.6\,keV in cS1 and cS2 has been measured to be 15.8\% and 14.7\%, respectively, and is used to extract the standard 
deviations $\sigma_{cs1}$, $\sigma_{cs2}$.  The correlation parameter is assumed to be independent of energy (at least in the considered narrow energy range) and measured
using the 164\,keV line from the decay of the $^{131m}$Xe isomer ($T_{1/2}$=11.8\,d) produced during the  $^{124}$AmBe run. This $\gamma$-line is chosen because it allows to disentangle efficiently the contribution from the nuclear recoil. The measured correlation coefficient is $\rho \, = \, -0.45 \pm 0.10$.

@@

{\textcolor{red} {Should we also give the numerical values of $L_Y$ and $Y$?}}
The pdf of the ER and NR contributions are then convoluted together to obtain the overall pdf of the expected signal.
A 2D (cS1 versus cS2) acceptance map is applied to the signal pdf to reproduce data selection effects. Acceptances are computed separately for each selection 
criteria using the $^{124}$AmBe calibration sample. Other selections such as the liquid xenon veto cut, and the single-scatter interaction represent an exception  and 
a dedicated computation has been performed in these cases. The combined acceptance  of all selection criteria in the region of interest averages to $\sim$$(0.80\pm0.05)$. 
Figure~\ref{fig:unc} shows an example of fully simulated signal model for a WIMP mass of 100\,GeV/c$^2$.

The signal simulation procedure has been validated by reproducing the 39.6\,keV xenon line from interactions due to neutrons from the 
$^{124}$AmBe source and comparison to data. For this comparison, the  $^{124}$AmBe nuclear recoil interactions and their acceptances
were simulated. The simulated events were in agreement  with calibration data within statistical uncertainties. 
{\textcolor{red} {Should we show an example, namely a figure from the signal model note?}}

@@

The expected background is modelled using data from the $^{60}$Co calibration campaign, which are assumed to well represent the background density distribution 
in the (cS1,cS2)-plane. The calibration sample yields  about $2.2\times10^4$ events in the ROI; these are then scaled to the science data according to a measured scale 
factor $\tau_{bkg}$. This scale factor, which is merely the ratio between the data and calibration sample yields, is measured in the two control regions shown in Figure~\ref{fig:SR} (labelled CR1 and CR2). The two control regions give compatible results and the computed average is $\tau_{bkg} \, =  \, 0.034 \pm 0.002 $, where the reported uncertainty 
is of statistical nature only.

### 2017-01-20 Inelastic/intro.tex
fixed_typos_and_some_text_added_more_comments_in_red

Most direct detection searches focus on elastic scattering of galactic dark matter particles off nuclei, where the keV-scale 
nuclear recoil energy is to be detected~\cite{Baudis:2012ig,Baudis:2015mpa,Undagoitia:2015gya}. In this work, the 
alternative process of inelastic scattering is explored, where a WIMP-nucleus scattering induces a transition to a low-lying 
excited nuclear state. The experimental signature is a nuclear recoil detected together with the prompt de-excitation 
photon~\cite{Ellis:1988nb}.

We consider the $^{129}\text{Xe}$ isotope, which has an abundance of 26.4\% in natural xenon, and a lowest-lying 
3/2$^{+}$ state at 36.6\,keV above the 1/2$^+$ gound state. The electromnagnetic nuclear decay has a half-life of 0.97\,s. 
The signatures of inelastic scattering in xenon have been studied in detail in~\cite{Baudis:2013bba}. It was found that this 
channel is complementary to spin-dependent, elastic scattering, dominating the integrated rates above $\simeq10$\,keV energy 
depositions. In addition, in case of a positive signal, the observation of inelastic scattering would provide a clear 
indication of the spin-dependent nature of the fundamental interaction.

Our paper is structures as follows.  In Section~\ref{sec:xenon100} we briefly describe the XENON100 detector and the employed data 
set in this analysis. In Section~\ref{sec:analysis} we detail the data analysis method, including the simulation of the expected signal and the 
background model. We conclude in Section~\ref{sec:results} with our results and new constraints on inelastic WIMP-nucleus scatters.

@@

The XENON100 experiment operates a dual-phase (liquid and gas) xenon time projection chamber (TPC) at the Laboratori Nazionali 
del Gran Sasso (LNGS) in Italy. It contains 161\,kg of xenon in total,  with  62\,kg in the active region of the TPC. These 
are monitored by 242 1-inch square, low-radioactivity, UV-sensitive photomultiplier tubes (PMTs) arranged in two arrays, one in the liquid 
and one in the gas. The PMTs detect the prompt scintillation (S1) and the delayed, proportional scintillation signal (S2) 
created by a particle interacting in the active TPC region. The S2-signal is generated due to ionisation electrons, drifted 
in an electric field of 530\,V/cm and extracted into the gas phase by a stronger field of $\sim$ 12\,kV/cm, where the proportional scintillation, or electroluminiscence, 
is produced. These photons carry the $(x,y)$ information of the interaction site, while the $z-$information comes from the drift time measurement. The TPC 
thus yields a three-dimensional event localisation, with an $(x,y)$ resolution of $<$3\,mm (1\,$\sigma$), and a $z$ resolution of  $<$0.3\,mm (1\,$\sigma$), enabling to reject the majority of background events via fiducial volume cuts~\cite{Aprile:2011dd}. The ratio S2/S1 provides the basis for distinguishing between nuclear recoils (NRs), as induced by fast neutrons and expected from elastic WIMP-nucleus scatters, and electronic recoils (ERs) produced by $\beta$ and $\gamma$-rays.

XENON100 has acquired science data between 2008-2015, and has set competitive constraints on spin-independent~\cite{Aprile:2012nq,Aprile:2016swn} 
and spin-dependent~\cite{Aprile:2013doa,Aprile:2016swn} elastic WIMP-nucleus 
scatters, on solar axions and galactic ALPs~\cite{Aprile:2014eoa}, as well as on leptophilic dark matter models~\cite{Aprile:2015ade,Aprile:2015ibr,Aprile:2017yea}.

Here we explore a potential new signature in the XENON100 detector, caused by spin-dependent, inelastic WIMP-$^{129}$Xe scatters. The expected  
inelastic scattering signature is a combination of an ER and a NR, due to the short lifetime of the excited nuclear state and  the short mean free path of $\sim$0.15\,mm of the 39.6\,keV de-excitation photon.

>>>>

Most direct detection searches focus on elastic scattering of galactic dark matter particles off nuclei, where the keV-scale 
nuclear recoil energy is to be detected~\cite{Baudis:2012ig,Undagoitia:2015gya,Baudis:2015mpa}. In this work, the 
alternative process of inelastic scattering is explored, where a WIMP-nucleus scattering induces a transition to a low-lying 
excited nuclear state. The experimental signature is a nuclear recoil detected together with the prompt de-excitation 
photon~\cite{Ellis:1988nb}.

We consider the $^{129}\text{Xe}$ isotope, which has an abundance of 26.4\% in natural xenon, and a lowest-lying 
3/2$^{+}$ state at 36.6\,keV above the 1/2$^+$ ground state. The electromagnetic nuclear decay has a half-life of 0.97\,s. 
The signatures and structure functions for inelastic scattering in xenon have been studied in detail in~\cite{Baudis:2013bba}. It was found that this channel is complementary to spin-dependent, elastic scattering, and that it dominates the integrated rates above $\simeq10$\,keV energy depositions. 
In addition, in case of a positive signal, the observation of inelastic scattering would provide a clear 
indication of the spin-dependent nature of the fundamental interaction.

This paper is structured as follows.  In Section~\ref{sec:xenon100} we briefly describe the main features of the XENON100 detector.  In Section~\ref{sec:analysis} we introduce the employed data 
set in this analysis and detail the data analysis method, including the simulation of the expected signal and the 
background model. We conclude in Section~\ref{sec:results} with our results, and discuss the new constraints on inelastic WIMP-nucleus interactions.

@@

The XENON100 experiment operates a dual-phase (liquid and gas) xenon time projection chamber (TPC) at the Laboratori Nazionali 
del Gran Sasso (LNGS) in Italy. It contains 161\,kg of xenon in total,  with  62\,kg in the active region of the TPC. These 
are monitored by 178 1-inch square, low-radioactivity, UV-sensitive photomultiplier tubes (PMTs) arranged in two arrays, one in the liquid 
and one in the gas. The PMTs detect the prompt scintillation (S1) and the delayed, proportional scintillation signal (S2) 
created by a particle interacting in the active TPC region. The S2-signal is generated due to ionisation electrons, drifted 
in an electric field of 530\,V/cm and extracted into the gas phase by a stronger field of $\sim$ 12\,kV/cm, where the proportional scintillation, or electroluminiscence, 
is produced. These photons carry the $(x,y)$ information of the interaction site, while the $z-$information comes from the drift time measurement. The TPC 
thus yields a three-dimensional event localisation, with an $(x,y)$ resolution of $<$3\,mm (1\,$\sigma$), and a $z$ resolution of  $<$0.3\,mm (1\,$\sigma$), enabling to reject the majority of background events via fiducial volume cuts~\cite{Aprile:2011dd}. The ratio S2/S1 provides the basis for distinguishing between nuclear recoils (NRs), as induced by fast neutrons and expected from elastic WIMP-nucleus scatters, and electronic recoils (ERs) produced by $\beta$ and $\gamma$-rays.  A 4\,cm thick liquid xenon (LXe) layer surrounds the TPC and is monitored by 64 1-inch square PMTs, providing an effective active veto for further background reduction.

XENON100 has acquired science data between 2008-2015, and has set competitive constraints on spin-independent~\cite{Aprile:2012nq,Aprile:2016swn} 
and spin-dependent~\cite{Aprile:2013doa,Aprile:2016swn} elastic WIMP-nucleus 
scatters, on solar axions and galactic ALPs~\cite{Aprile:2014eoa}, as well as on leptophilic dark matter models~\cite{Aprile:2015ade,Aprile:2015ibr,Aprile:2017yea} that were invented to explain the annual modulation signature observed in the DAMA/LIBRA experiment~\cite{Bernabei:2012in}.

Here we explore a new potential dark matter channel in the XENON100 detector, caused by spin-dependent, inelastic WIMP-$^{129}$Xe interactions. The expected inelastic scattering signature is a combination between an ER and a NR, due to the short lifetime of the excited nuclear state and  the short mean free path of $\sim$0.15\,mm of the 39.6\,keV de-excitation photon.

### 2017-01-20 Inelastic/results.tex
fixed_typos_and_some_text_added_more_comments_in_red

This result is interpreted via a binned profiled likelihood approach by means of the test statistic $\tilde{q}$
and its asymptotic distributions, as  described in \cite{asympt}. 
Assuming  an isothermal WIMP halo with a local density of $\rho_{\chi} \, = \, 0.3$\,GeV/cm$^3$, a local circular velocity of $v_0 \,= \, 220$\,km/s, and a galactic escape velocity of $v_{\rm{esc}} \, = \, 544$\,km/s, 
\textcolor{blue}{other assumptions...,} a 90\% CL$_s$~\cite{cls} confidence level upper limit on the spin-dependent inelastic WIMP-nucleon cross section as a function of WIMP mass is computed. We employ the nuclear structure factors as calculated in \cite{Baudis:2013qla}, based on state-of-the-art large-scale shell-model calculations, with chiral effective field theory WIMP-nucleon currents.

@@

Our result is shown in Figure~\ref{fig:limits}, together with the expected median sensitivity and its relative one and two  standard deviation uncertainty.
The most constraining upper limit is  $3.3 \times 10^{-38}$\,cm$^{2}$ (at 90\% CL$_s$ confidence level) is for a WIMP of mass 100\,GeV/c$^2$.

@@

Our limit improves upon the XMASS result and constrains new parameter space for the spin-dependent, inelastic scattering cross section. While these upper limits are not competitive to spin-dependent, elastic scattering results, as obtained by XENON100~\cite{Aprile:2013doa} and LUX~\cite{Akerib:2016lao} (with a cross section minimum of $\sim2 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/cm$^2$ WIMP), our results set the pathway for a sensitive search of inelastic WIMP-nucleus scattering in running or upcoming liquid xenon experiments such as XENON1T~\cite{Aprile:2015uzo}, XENONnT~\cite{Aprile:2015uzo},  LZ~\cite{Akerib:2015cja}, and DARWIN~\cite{Aalbers:2016jon}. In these larger detectors, with lower intrinsic backgrounds from $^{85}$Kr and $^{222}$Rn decays, and improved self-shielding, the electronic recoil background will be reduced by a few orders of magnitude with respect to XENON100, and ultimately dominated by solar neutrino interactions~\cite{Baudis:2013qla}.

The discovery of this interaction channel would be a clear signature for a spin-dependent nature of the interaction, and would provide a potential handle  to constrain the WIMP mass~\cite{Baudis:2013bba}.

>>>>

{\textcolor{red} {Should we first say that we do not observe any signal, given that the observed rate is compatible with the expected background?}}
This result is interpreted via a binned profiled likelihood approach by means of the test statistic $\tilde{q}$
and its asymptotic distributions, as  described in \cite{asympt}. 
Assuming  an isothermal WIMP halo with a local density of $\rho_{\chi} \, = \, 0.3$\,GeV/cm$^3$, a local circular velocity of $v_0 \,= \, 220$\,km/s, and a galactic escape velocity of $v_{\rm{esc}} \, = \, 544$\,km/s, 
\textcolor{blue}{other assumptions...,} a 90\% CL$_s$~\cite{cls} confidence level upper limit on the spin-dependent inelastic WIMP-nucleon cross section as a function of WIMP mass is computed. We employ the nuclear structure factors as calculated in \cite{Baudis:2013qla}, based on state-of-the-art large-scale shell-model calculations, with chiral effective field theory WIMP-nucleon currents.

@@

Our result is shown in Figure~\ref{fig:limits}, together with the expected median sensitivity and its relative one and two  standard deviation uncertainty.
The most constraining upper limit is  at a cross section of $3.3 \times 10^{-38}$\,cm$^{2}$ (at 90\% CL$_s$ confidence level), for a WIMP of mass 100\,GeV/c$^2$.

@@

Our limit improves upon the XMASS result and constrains new parameter space for the spin-dependent, inelastic scattering cross section. While these upper limits are not competitive to spin-dependent, elastic scattering results, as obtained by XENON100~\cite{Aprile:2013doa} and LUX~\cite{Akerib:2016lao} (with a cross section minimum of $\sim2 \times 10^{-40}$\,cm$^{2}$, at 90\% C.L.,  for a 100\,GeV/c$^2$ WIMP), our results set the pathway for a sensitive search of inelastic WIMP-nucleus scattering in running or upcoming liquid xenon experiments such as XENON1T~\cite{Aprile:2015uzo}, XENONnT~\cite{Aprile:2015uzo},  LZ~\cite{Akerib:2015cja}, and DARWIN~\cite{Aalbers:2016jon}. In these larger detectors, with lower intrinsic backgrounds from $^{85}$Kr and $^{222}$Rn decays, and improved self-shielding, the electronic recoil background will be reduced by a few orders of magnitude with respect to XENON100, and ultimately dominated by solar neutrino interactions~\cite{Baudis:2013qla}. 
The discovery of this interaction channel would be a clear signature for a spin-dependent nature of the interaction, and would provide a potential handle  to constrain the WIMP mass with data from one experiment only~\cite{Baudis:2013bba}.

\newpage
